Summary: Dec. 1 Committee Meeting

### 2018-01-07 Graphing+Analysis.Rmd
1/6

```{r}
ggplot(data,aes(x=scar.BM,y=FR))+facet_grid(.~Species)+geom_smooth(method="lm")+geom_point(shape=18)+ggtitle("Feeding rate by scarid biomass") + theme_minimal() +labs(y="Feeding rate (bites/hr)",x="Scarid Biomass (g/100m2)") + theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r,echo=FALSE,warning=FALSE}
ggplot(data,aes(x=scar.BM,y=FR,colour=Phase))+facet_grid(.~Species)+geom_point(shape=18)+geom_smooth(method=lm, fullrange=FALSE)+ggtitle("Feeding rate by phase and scarid biomass") + theme_minimal() +labs(y="Feeding rate (bites/hr)",x="Scarid Biomass (g/100m2)") + theme(plot.title = element_text(hjust = 0.5)) + scale_color_manual(values=c("gray40", "aquamarine3"))
```

@@

plot(pca,type="l")
ggbiplot(pca, obs.scale = 1, var.scale = 1, groups=site.sum$Island, ellipse = TRUE, circle = TRUE, varname.size = 2) + scale_color_manual(name="Island", values=c("navy", "darkseagreen", "slategray2")) + theme(legend.direction = 'horizontal', legend.position = 'top') + theme_minimal()

```
### Benthic variables
```{r}
predictors1 <- site.sum %>% select(cover_LC,cover_TA,canopy_MA,canopy_TA,rugosity) # should it matter if I use site level summary data vs. full follow dataset (where site-level data has been joined?)
pca1 <- prcomp(na.omit(predictors1),center = TRUE,scale. = TRUE) 
summary(pca1)

plot(pca1,type="l")
ggbiplot(pca1, obs.scale = 1, var.scale = 1, groups=site.sum$Island, ellipse = TRUE, circle = TRUE, loadings.label.repel=TRUE) + scale_color_manual(name="Island", values=c("navy", "darkseagreen", "slategray2")) + theme(legend.direction = 'horizontal', legend.position = 'top') + theme_minimal()

# add PC1 and PC2 as variables in dataset
pca1.scores <- as.data.frame(pca1$x) %>% select(PC1,PC2)
site.sum <- site.sum  %>% bind_cols(pca1.scores)
pca1.scores <- select(site.sum,Site,PC1,PC2)
data <- data %>% left_join(pca1.scores,by="Site")
```
### Fish community variables
```{r}
predictors2 <- site.sum %>% select(scar.BM,scar.DEN,carn.BM) # should it matter if I use site level summary data vs. full follow dataset (where site-level data has been joined?)
pca2 <- prcomp(na.omit(predictors2),center = TRUE,scale. = TRUE) 
summary(pca2)

@@

### Feeding rates
```{r}
initial<-data%>%filter(Phase=="i") # for analysis with initial only
lm_FR <- lm(FR~scar.BM*Species+carn.BM+Length.cm+PC1+PC2, data=data)
summary(lm_FR)
#vif(lm_FR)
```
*Notes: nearly everything is significant? Significant interaction between scar.BM and species for Spar. viride. carn.BM and scar.BM are highly positively correlated (~0.86) - is it ok to include both?*
*R2 goes up slightly with initial only*

### Fraction of time grazing
```{r}
lm_g.frac <- lm(g.frac~Species*scar.BM+scar.DEN+carn.BM+Phase+Length.cm+PC1+PC2, data=data)
summary(lm_g.frac)
```
*Notes: carn.BM and PC1 are strongest predictors of time spent grazing, scar.BM and phase are also significant. Slight significance of species, length, and species-scar.BM interaction*

@@

```{r}
lme_FR_rbp <- lme(FR~Phase+Length.cm+scar.BM+scar.DEN+carn.BM+PC1+PC2,data=rbp,random=~1|Island, na.action = na.omit)
summary(lme_FR_rbp)
```
*Notes: much more variable, less predictable. Maybe take out of overall analysis?*
------------------------
To Do as of Nov. 7
* ~~incorporate PCs~~
* boosted regression trees ecosphere 2017 adrians paper
* ~~simpler graphs with just herb density x axis - grazing behaviors y, facet by species~~
* ~~Species*density as fixed effect~~
* Species as random effect
* ~~break out species and run separately~~

>>>>

```{r}
anubon <- data %>% filter(Island!="Barbuda")
ggplot(anubon,aes(x=scar.BM,y=FR))+facet_grid(.~Species)+geom_smooth(method="loess")+geom_point(shape=18)+ggtitle("Feeding rate by scarid biomass") + theme_minimal() +labs(y="Feeding rate (bites/hr)",x="Scarid Biomass (g/100m2)") + theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r,echo=FALSE,warning=FALSE}
ggplot(data,aes(x=scar.BM,y=FR,colour=Phase))+facet_grid(.~Species)+geom_point(shape=18)+geom_smooth(method=loess, fullrange=FALSE)+ggtitle("Feeding rate by phase and scarid biomass") + theme_minimal() +labs(y="Feeding rate (bites/hr)",x="Scarid Biomass (g/100m2)") + theme(plot.title = element_text(hjust = 0.5)) + scale_color_manual(values=c("gray40", "aquamarine3"))
```

@@

plot(pca,type="l")
ggbiplot(pca, obs.scale = 1, var.scale = 1, groups=site.sum$Island, ellipse = TRUE, circle = TRUE, varname.size = 2) + scale_color_manual(name="Island", values=c("navy", "darkseagreen", "slategray2")) + theme(legend.direction = 'horizontal', legend.position = 'top') + theme_minimal()
```
### Benthic variables
```{r, echo=FALSE}
pred.benthic <- site.sum %>% select(cover_LC,cover_TA,canopy_MA,canopy_TA,rugosity) # should it matter if I use site level summary data vs. full follow dataset (where site-level data has been joined?)
pca1 <- prcomp(na.omit(pred.benthic),center = TRUE,scale. = TRUE)

ggbiplot(pca1, obs.scale = 1, var.scale = 1, groups=site.sum$Island, ellipse = TRUE, circle = TRUE, loadings.label.repel=TRUE, varname.size=2.5, varname.adjust=1.1) + scale_color_manual(name="Island", values=c("navy", "darkseagreen", "slategray2")) + theme(legend.direction = 'horizontal', legend.position = 'top') + theme_minimal()

# add PC1 and PC2 as variables in dataset
pca1.scores <- as.data.frame(pca1$x) %>% select(PC1,PC2)
site.sum <- site.sum  %>% bind_cols(pca1.scores)
pca1.scores <- select(site.sum,Site,PC1,PC2)
data2 <- data %>% left_join(pca1.scores,by="Site")

setwd("~/github/Scarid-Behavior/data")
write.csv(data2,file = "data2.csv")
```
### Fish community variables
```{r}
pred.fish <- site.sum %>% select(scar.BM,scar.DEN,carn.BM) # should it matter if I use site level summary data vs. full follow dataset (where site-level data has been joined?)
pca2 <- prcomp(na.omit(pred.fish),center = TRUE,scale. = TRUE) 
summary(pca2)

@@

### Feeding rates
```{r}
initial<-data%>%filter(Phase=="i") # for analysis with initial only
lm_FR <- lm(FR~scar.BM*Species+Phase+carn.BM+Length.cm+PC1+PC2, data=data)
summary(lm_FR)
#vif(lm_FR)
```
*Notes: nearly everything is significant? Significant interaction between scar.BM and species for Spar. viride. carn.BM and scar.BM are highly positively correlated (~0.86) - is it ok to include both?*
*R2 goes up slightly with initial only*

### Fraction of time grazing
```{r}
lm_g.frac <- lm(g.frac~Species*scar.BM+Phase+scar.DEN+carn.BM+Phase+Length.cm+PC1+PC2, data=data)
summary(lm_g.frac)
```
*Notes: carn.BM and PC1 are strongest predictors of time spent grazing, scar.BM and phase are also significant. Slight significance of species, length, and species-scar.BM interaction*

@@

```{r}
lme_FR_rbp <- lme(FR~Phase+Length.cm+scar.BM+scar.DEN+carn.BM+PC1+PC2,data=rbp,random=~1|Island, na.action = na.omit)
summary(lme_FR_rbp)
```
*Notes: much more variable, less predictable. Maybe take out of overall analysis?*

## GAMs

```{r, echo=FALSE}
vet<-data %>% filter(Species.Code=="qup")
gamvet<-gam(FR~Phase+s(Length.cm)+s(scar.BM)+(carn.BM)+(PC1)+(PC2), family=gaussian(link=identity),data=vet, method="REML")
summary(gamvet)
plot(gamvet)
```
```{r, echo=FALSE}
vir<-data %>% filter(Species.Code=="stop" & Site!="Snapper Point")
gammvir<-gamm(FR~Phase+s(Length.cm)+s(scar.BM)+s(carn.BM)+s(PC1)+s(PC2), family=gaussian(link=identity),data=vir, random=list(Island=~1),method="REML")
summary(gammvir)
plot(gammvir)
```
------------------------
To Do as of Nov. 7
* ~~incorporate PCs~~
* boosted regression trees ecosphere 2017 adrians paper
* ~~simpler graphs with just herb density x axis - grazing behaviors y, facet by species~~
* ~~Species*density as fixed effect~~
* Species as random effect
* ~~break out species and run separately~~

### 2018-01-07 Summary.Rmd
1/6

---
title: "Dec. 1 Committee Meeting"
author: "Molly Wilson"
date: "12/1/2017"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
    toc_float: yes
    toc_depth: 3
  pdf_document:
    toc: yes
---

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
setwd("~/Google Drive/Research + Projects/Dissertation/ABB_Grazing/Analysis")
library(rmarkdown)
library(dplyr)
library(tidyr)
library(lazyeval)
library(ggplot2)
library(ellipse)
library(RColorBrewer)
library(ggbiplot)
library(nlme)
library(pls)
```
```{r,message=FALSE,warning=FALSE, echo=FALSE}
site.sum <- read.csv("site.sum.csv", stringsAsFactors=FALSE) %>% select(-X)
data <- read.csv("sumID2.csv", stringsAsFactors=FALSE) %>% select(Island,Site,Spearfishing,Diving,Species,Species.Code,Phase,Length.cm,g.frac,FR,BR,TDB,for.dur,for.bites,tot.BM,tot.DEN,scar.BM,herb.BM,scar.DEN,conspec.BM,conspec.DEN,carn.BM,carn.DEN,cover_CCA,cover_LC,cover_MA,cover_TA,canopy_MA,canopy_TA,rugosity,int.tot,int.con,int.hetscar,int.dam)
vetvir <- data %>% filter(Species.Code!="rbp")
vetvir20 <- vetvir %>% filter(Length.cm>=15 & Length.cm<=25)
init20<- vetvir %>% filter(Length.cm>=15 & Length.cm<=25 & Phase=="i")
```

@@

@@

### Grazing PCAs

@@

```{r,echo=FALSE}
response <- vetvir %>% select(g.frac,FR,BR)
log.vars5 <- log(response[,1:3])
pca3 <- prcomp(na.omit(response),center = TRUE,scale. = TRUE) 
ggbiplot(pca3, obs.scale = 1, var.scale = 1, groups=vetvir$Island,ellipse = TRUE, circle = TRUE, alpha=0.8,varname.size = 5) + theme_minimal() + scale_color_manual(name="Island", values=c("navy", "darkseagreen", "slategray2")) + labs(title="Grazing behaviors by island") + theme(plot.title = element_text(hjust = 0.5))
```

>>>>

---
title: "Summary: Dec. 1 Committee Meeting"
author: "Molly Wilson"
date: "12/1/2017"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
    toc_float: yes
    toc_depth: 3
  pdf_document:
    toc: yes
---

```{r,message=FALSE,warning=FALSE, echo=FALSE}
# set up
library(rmarkdown)
library(dplyr)
library(tidyr)
library(lazyeval)
library(ggplot2)
library(ellipse)
library(RColorBrewer)
library(ggbiplot)
library(nlme)
library(pls)
```
```{r,message=FALSE,warning=FALSE, echo=FALSE}
setwd("~/github/Scarid-Behavior/data")
site.sum <- read.csv("site.sum.csv", stringsAsFactors=FALSE) %>% select(-X)
data <- read.csv("sumID2.csv", stringsAsFactors=FALSE) %>% select(Island,Site,Spearfishing,Diving,Species,Species.Code,Phase,Length.cm,g.frac,FR,BR,TDB,for.dur,for.bites,tot.BM,tot.DEN,scar.BM,herb.BM,scar.DEN,conspec.BM,conspec.DEN,carn.BM,carn.DEN,cover_CCA,cover_LC,cover_MA,cover_TA,canopy_MA,canopy_TA,rugosity,int.tot,int.con,int.hetscar,int.dam)
vetvir <- data %>% filter(Species.Code!="rbp")
vetvir20 <- vetvir %>% filter(Length.cm>=15 & Length.cm<=25)
init20<- vetvir %>% filter(Length.cm>=15 & Length.cm<=25 & Phase=="i")
```

@@

### Grazing behaviors by island
```{r,echo=FALSE}
response <- vetvir %>% select(g.frac,FR,BR)
log.vars5 <- log(response[,1:3])
pca3 <- prcomp(na.omit(response),center = TRUE,scale. = TRUE) 
ggbiplot(pca3, obs.scale = 1, var.scale = 1, groups=vetvir$Island,ellipse = TRUE, circle = TRUE, alpha=0.8,varname.size = 5) + theme_minimal() + scale_color_manual(name="Island", values=c("navy", "darkseagreen", "slategray2")) + labs(title="Grazing behaviors by island") + theme(plot.title = element_text(hjust = 0.5))
```

*BOXPLOTS*

@@

@@
